Quality Assesment of OpenStreetMap Footpath Data for 3D City Modelling

### 2020-05-07 report/report.tex
Reorganize implementation
Shorten abstract

This project assesses the feasibility of creating a 3D representation of OpenStreetMap (OSM) geodata with the inclusion of pedestrian footpaths, by focusing on OSM road and building data in the Stockholm metropolitan area.
\\
An estimate of the positional accuracy of OSM data has been obtained by comparing OSM positional data to a dataset with a known accuracy, which was obtained from the Swedish National Land Survey.
It was found that the average positional error in the OSM dataset was about 2 meters, and approximately 98\% of all buildings in the reference dataset were represented in the OSM dataset.
\\
This estimate of the positional error was used to assess the integrity of the OSM Stockholm road network, by locating critical points where extending the roads and paths with indivdual widths would cause collision with other features.
An algortitm then took the road network and made adjustments that were within the found margin of error for the OSM dataset, to eliminate as many collisions as possible.
It was found that extending all roads with a standard width led to collisions between roughly 12\% of all roads in the dataset.
The total length of road that intersected with other features was less than 0.1\% of the total road length.
It was measured that roughly 80\% of these colliding features could be corrected by simple geometrical translation by a distance smaller than the posiional accuracy of the OSM dataset.
Similarily, the amount of colliding road by length that could be corrected was calculated to around 99\%.
It was found that footpaths were much less problematic than other road types (primary, secondary, residential), in terms of feature collisions.
\\
The report concludes with a discussion of the findings of this study, and an assessment of the feasibility of generating city models with pedestrian footpaths in a number of different applications from urban planning tools to videogames.
As secondary contributions, the completeness and shape accuracy of the OSM data set have also been estimated and commented.

@@

\section{Dataset quality evaluation}

@@

\section{Implementation}

In this implementation, roads of different types were allowed to merge into one another to form common intersections. To facilitate this, it was neccessary to work with a path-by-path representation of the point data. When two path share a node with common coordinates, they form an intersection which can be of multiple different types.

% TODO: Write disposition for implementation of the collision checker

\section{Notes about data processing}

@@

>>>>

This project assesses the feasibility of creating a 3D representation of OpenStreetMap (OSM) geodata with the inclusion of pedestrian footpaths, by focusing on OSM road and building data in the Stockholm metropolitan area.
\\
An estimate of the positional accuracy of OSM data has been obtained by comparing OSM positional data to a dataset with a known accuracy, which was obtained from the Swedish National Land Survey.
It was found that the average positional error in the OSM dataset was about 2 meters, and approximately 98\% of all buildings in the reference dataset were represented in the OSM dataset.
\\
This estimate of the positional error was used to assess the integrity of the OSM Stockholm road network, by locating critical points where assigning widths to the roads would cause collision with other features.
An algortitm then took the road network and made adjustments that were within the found margin of error for the OSM dataset, to eliminate as many collisions as possible.
It was found that extending all roads with a standard width led to collisions between roughly 12\% of all roads in the dataset.
The total length of road that intersected with other features was less than 0.1\% of the total road length.
It was measured that roughly 80\% of these colliding features, and 99\% of the colliding road by length, could be corrected by simple geometrical translation by a distance smaller than the posiional accuracy of the OSM dataset.
It was found that footpaths were much less problematic than other road types (primary, secondary, residential), in terms of feature collisions.
\\
The report concludes with a discussion of the findings of this study, and an assessment of the feasibility of generating city models with pedestrian footpaths in a number of different applications from urban planning tools to videogames.
As secondary contributions, the completeness and shape accuracy of the OSM data set have also been estimated and commented.

@@

@@

\subsection{Notes about data processing}

@@

% TODO: Write disposition for implementation of the collision checker
In this implementation, roads of different types were allowed to merge into one another to form common intersections. To facilitate this, it was neccessary to work with a path-by-path representation of the point data. When two path share a node with common coordinates, they form an intersection which can be of multiple different types.
